% import custom functions
\input{functions.tex}

\settopoffset{0}
\setname{Liam}{Beguin}
\setjob{Junior software developer}
\def\slist{Linux, Git, Embedded systems, Yocto, Neural networks, C, Bash,
		   \LaTeX, Kernel device drivers, Unmanned Aerial Systems, Robotics,
		   Altium Designer}

% Set pdf metadata
\hypersetup{
	pdftitle    = {\name: \job},
	pdfsubject  = {\job},
	pdfauthor   = {\name},
	pdfcreator  = {\name},
	pdfkeywords = {\slist},
}

\begin{document}
	\thispagestyle{empty} % remove page number
	\drawframe % set background colors

	%--------------------------------------------------------------------------
	%	LEFT COLUMN
	%--------------------------------------------------------------------------

	\begin{textblock}{\sidebarwidth}(0.5, 0.5)
		\namesection

		\customsectionleft{Informations}

		\info{location1}{Montreal, CA}
		\\ \info{social}{@liambeguin}
		\\ \info{language}{french, english}
		\\ \info{phone1}{(514) 430-8113}
		\\ \info{email1}{\href{mailto:liambeguin@gmail.com}{liambeguin@gmail.com}}
		% \\ \info{car}{driver's license, no car}
		\vspace{0.6cm}

		\customsectionleft{Summary}

		During my work as an embedded software developer, I had the chance to
		improve my software skills (C, Bash, Python) and learn a lot about
		embedded software architecture. Next, I'd like to improve my knowledge
		of the Linux kernel and start working with the community. Working with
		others, I realized that I could rapidly adapt to new objectives and
		constraints set by the industry. I am mostly known for my scientific
		curiosity and my autonomy.
		\vspace{1cm}

		\customsectionleft{General Skills}

		\begin{tabular}{ll}
			Bash          & \showdots{7} \\
			Yocto         & \showdots{6} \\
			Git           & \showdots{5} \\
			C             & \showdots{7} \\
			Python        & \showdots{6} \\
			Linux kernel  & \showdots{3} \\
			Vim           & \showdots{7} \\
		\end{tabular} \\ \\

		\drawslist{}

	\end{textblock}



	%--------------------------------------------------------------------------
	%	RIGHT COLUMN
	%--------------------------------------------------------------------------
	\begin{textblock}{13.5}(7.5, 0.5)
		\customsectionright{Experiences}

		\jobtitle{Xiphos Systems Corporation}{Montreal, CA}
		Dedicated mainly to space applications, {\em Xiphos Systems} offers hybrid
		logic and software solutions, providing capabilities for controlling
		various payloads and adapting existing algorithms in order to improve
		performance.

		\begin{description}
			\item[Keywords:] Yocto, Linux shell, Linux kernel, U-Boot, Git, Xilinx zynq, gcc
			\item[Junior software developer - Part-time] \dotfill 05/2015 to \emph{today}
				\subitem{Embedded software design}
				\subitem{Build system maintenance}
			\item[Junior software developer - Internship] \dotfill 09/2014 to 04/2015
				\subitem{Quality assurance}
		\end{description}

		\jobtitle{HiKoB}{Grenoble, FR}
		{\em HiKoB}'s mission is to develop and provide wireless autonomous multi points
		data acquisition systems to capture information on the field.

		\begin{description}
			\item[Keywords:] Altium designer, STM32, Git, openlab, C, IMU
			\item[Junior software developer - Internship] \dotfill 04/2013 to 07/2013
				\subitem{Printed Circuit Board (PCB) design}
				\subitem{Embedded software development}
		\end{description}

		\customsectionright{Projects}

		\jobtitle{Dronolab}{Montreal, CA}
		The main goal of this student club is to design and operate autonomous multicopters.
		These Unmanned Aerial Vehicles (UAVs) can then be used to perform aerial surveys for
		civil applications.

		\begin{description}
			\item[Keywords:] Altium designer, STM32, Control theory, Yocto, Linux, iMX6
			\item[Responsibilities] \hfill
				\subitem{Printed Circuit Board (PCB) design}
				\subitem{Software development and maintenance for the autopilot and it's payload}
				\subitem{Competition crew member at \emph{Unmanned Systems Canada} (2014, 2015)}
				\subitem{Competition crew member at \emph{AUVSI Seafarer} (2015)}
		\end{description}

		\customsectionright{Education}

			\centerline{\textbf{\large{Bachelor of science in Electrical Engineering }}}
			\'Ecole de Technologie Sup\'erieure (ETS) \textbullet{} Montreal, CA \dotfill 09/2013 to 12/2017 \\

			\centerline{\textbf{\large{College diploma in electronics and Computer Science}}}
			University Joseph Fourier \textbullet{} Grenoble, FR \dotfill 09/2011 to 07/2013 \\
	\end{textblock}
\end{document}
% vim: cc=80
